Fast gravitational wave parameter estimation without compromises

### 2023-02-06 src/tex/ms.tex
add reference for heterodyned likelihood
Add Lee 2022 reference

% Effort going to new tools development.
In order to address this, there are efforts from multiple groups to speed up the
PE process. This includes methods that employ modern techniques such as
leveraging adaptive proposal distribution in nested sampling
\cite{Williams:2021qyt}, deep learning networks pre-trained on large collections
of waveforms \cite{Dax:2021tsq,Dax:2022pxd}, as well as methods that reduce the
computational expense of classical PE by leveraging our knowledge of GW signals
\cite{Islam:2022afg,Roulet:2022kot}. While these avenues are promising for
standard GW problems, they rely on assumptions that may not hold for analyses
targeting additional physical effects beyond standard CBCs in GR, such as
lensing and deviations from GR, or may use approximations that do not compute
the Bayesian likelihood exactly.

@@

Since the computational cost of evaluating a waveform model scales linearly
with the number of time or frequency bins, the computational burden for
longer-duration signals is often quite large. To mitigate this, there are a
number of methods to reduce the number of basis points needed to compute the
likelihood faithfully \cite{Field:2011mf, Field:2013cfa, Smith:2016qas,
Vinciguerra:2017ngf,Morisaki:2020oqk,Morisaki:2021ngj}. In this work, we take advantage of likelihood
heterodyning \cite{Cornish:2021lje} (also known as relative binning
\cite{Zackay:2018qdy}).

@@

% Compared to other works
There have been several recent efforts to speed up GW parameter estimation,
relying on techniques ranging from efficient reparameterizations
\cite{Islam:2022afg,Roulet:2022kot} to deep learning
\cite{Dax:2021tsq,Dax:2022pxd}. While all of these methods can achieve
minutes-scale parameter estimation with high fidelity under some conditions,
our approach possesses unique strengths, and may complement some of those other
techniques.

>>>>

% Effort going to new tools development.
In order to address this, there are efforts from multiple groups to speed up the
PE process. This includes methods that employ modern techniques such as
leveraging adaptive proposal distribution in nested sampling
\cite{Williams:2021qyt}, deep learning networks pre-trained on large collections
of waveforms \cite{Dax:2021tsq,Dax:2022pxd}, as well as methods that reduce the
computational expense of classical PE by leveraging our knowledge of GW signals
\cite{Islam:2022afg,Roulet:2022kot,Lee:2022jpn}. While these avenues are promising for
standard GW problems, they rely on assumptions that may not hold for analyses
targeting additional physical effects beyond standard CBCs in GR, such as
lensing and deviations from GR, or may use approximations that do not compute
the Bayesian likelihood exactly.

@@

Since the computational cost of evaluating a waveform model scales linearly
with the number of time or frequency bins, the computational burden for
longer-duration signals is often quite large. To mitigate this, there are a
number of methods to reduce the number of basis points needed to compute the
likelihood faithfully \cite{Field:2011mf, Field:2013cfa, Smith:2016qas,
Vinciguerra:2017ngf,Morisaki:2020oqk,Morisaki:2021ngj}. In this work, we take advantage of likelihood
heterodyning \cite{Cornish:2010kf,Cornish:2021lje} (also known as relative binning
\cite{Zackay:2018qdy}).

@@

% Compared to other works
There have been several recent efforts to speed up GW parameter estimation,
relying on techniques ranging from efficient reparameterizations
\cite{Islam:2022afg,Roulet:2022kot, Lee:2022jpn} to deep learning
\cite{Dax:2021tsq,Dax:2022pxd}. While all of these methods can achieve
minutes-scale parameter estimation with high fidelity under some conditions,
our approach possesses unique strengths, and may complement some of those other
techniques.
